---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# meps

This package contains a data set of all members of the European Parliament, 
for all parliamentary terms (1 through 8).

Please cite as follows:

> Nicolò Fraccaroli, Alessandro Giovannini, Jean-François Jamet, Eric Persson,
> Ideology and monetary policy. The role of political parties’ stances in the European Central > Bank’s parliamentary hearings,
> European Journal of Political Economy,
> 2022,
> 102207,
> ISSN 0176-2680,
> https://doi.org/10.1016/j.ejpoleco.2022.102207.

## Installation

You can install the development version with:

```r
devtools::install_github("expersso/meps")
```

## Example

```{r}
library(tibble)
library(meps)
head(meps)
```

Note that the last two columns are lists of data frames, and may not print 
properly without the `tibble` package. See the documentation `?meps::meps` for
explanations of what information these columns contain.
